Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
Small updates

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Distributed systems offer notable benefits over centralized ones.
  Reaping these benefits, however, requires programming in a way that makes distribution explicit---\eg via new programming languages, distributed frameworks, or source-level annotations.
  This paper presents \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
  \sys's insight is that shell pipelines already express stream computations that can be automatically distributed.
  To achieve this, \sys
decomposes primitives into distributability classes,
identifies high-distributability stages,
applies rewriting rules for largest possible subprograms,
and orchestrates the distributed program.
Its runtime component provides orchestration and planning support during the execution of the program.
Experiments for complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
\end{abstract}

% These are from the abstract:
%  with regards to the sequential program.
  % leveraging the insight that such programs already express stream computations, with their stages falling under a few, known distributability classes.
% a series of techniques for automatically 
% 
% Key challenges include 
% surprisingly expressive, 
% maximally distributable subprograms
%

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Distributed systems offer notable benefits over centralized ones.
  Reaping these benefits, however, requires programming in a way that makes distribution explicit---\eg via new programming languages, distributed frameworks, or source-level annotations.
  This paper presents \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
  Its insight is that pipelines already express stream computations that can be automatically distributed.
  To distribute them, \sys
    decomposes primitives into distributability classes,
    identifies high-distributability stages,
    applies rewriting rules for largest possible subprograms,
    and orchestrates the execution of the distributed program.
Experiments for complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
\end{abstract}

% Its runtime component provides orchestration and planning support during the execution of the program.
% These are from the abstract:
%  with regards to the sequential program.
  % leveraging the insight that such programs already express stream computations, with their stages falling under a few, known distributability classes.
% a series of techniques for automatically 
% 
% Key challenges include 
% surprisingly expressive, 
% maximally distributable subprograms
%
